### 2017-12-23 example-short-chapter.tex
Revert "failure change"
This reverts commit 5ba183bd5c87ddda4cc8dde6a2f3c5d085a17602.

	\item \textbf{Economic conditions.}
	Finally, another major factor that influences dividend policies is the market environment. If a certain sector is having trouble and anticipates profits falling, it's common for companies to get quite defensive when it comes to their dividends.\\	
	This can be seen currently in the energy sector, where low oil prices have wreaked havoc on many companies' profitability, which has led to several major companies slashing their dividends recently\footnote{JD.com, Inc. annual report 2016, Page 130}.
\end{itemize}

As for JD.com, inc, it stated that the form, frequency and amount of dividend payment will depend upon its future operations and earnings, capital requirements and surplus, general financial condition, contractual restrictions and other factors that the board of directors may deem.

\section{Dividend Policy performed by JD.com}
JD.com, inc does not reflect an active attitudes towards dividend payment. So far JD.com have not declared or paid any dividends on ordinary shares, nor do JD.com have any present plan to pay any cash dividends on ordinary shares in the foreseeable future.

\chapter{Current Assets and Current Liabilities}

\begin{center}

Current Assets (In thousands of RMB\textyen)

	\begin{tabular}{lrr}
		\toprule
		Fiscal year&2015&2016\\
		\midrule
		Short-term borrowings&17,863,868&19,771,695\\
		Nonrecourse securitization debt&2,114,913&4,391,955\\
		Accounts payable&2,780,482&4,391,955\\
		Advance from customers&-&723,449\\
		Deferred revenues&8,193,665&17,464,408\\
		Taxes payable&927,177&1,423,736\\
		Amount due to related parties&20,539,543&28,909,438\\
		Accrued expenses and other current liabilities&3,698,488&12,697,915\\
		Total current liabilities&-&10,766,920\\
		\bottomrule
	\end{tabular}
\end{center}

\begin{center}

Current Liabilities (In thousands of RMB\textyen)

\begin{tabular}{lrr}
	\toprule
	Fiscal year&2015&2016\\
	\midrule
	Cash and cash equivalents&17,863,868&19,771,695\\
	Restricted cash&2,114,913&4,391,955\\
	Short-term investments&2,780,482&4,391,955\\
	Investment securities&-&723,449\\
	Accounts receivable, net&8,193,665&17,464,408\\
	Advance to suppliers&927,177&1,423,736\\
	Inventories, net&20,539,543&28,909,438\\
	Loan receivables, net&3,698,488&12,697,915\\
	Other investments&-&10,766,920\\
	Prepayments and other current assets&1,486,441&2,198,906\\
	Amount due from related parties&863,516&1,410,050\\
	\bottomrule
\end{tabular}
\end{center}

>>>>

	\item \textbf{Economic conditions.}
	Finally, another major factor that influences dividend policies is the market environment. If a certain sector is having trouble and anticipates profits falling, it's common for companies to get quite defensive when it comes to their dividends.\\	
	This can be seen currently in the energy sector, where low oil prices have wreaked havoc on many companies' profitability, which has led to several major companies slashing their dividends recently.
\end{itemize}

As for JD.com, Inc., it stated that the form, frequency and amount of dividend payment will depend upon its future operations and earnings, capital requirements and surplus, general financial condition, contractual restrictions and other factors that the board of directors may deem\footnote{JD.com, Inc. annual report 2016, Page 130}.

\section{Dividend Policy performed by JD.com}
JD.com, Inc. does not reflect an active attitudes towards dividend payment. So far JD.com have not declared or paid any dividends on ordinary shares, nor do JD.com have any present plan to pay any cash dividends on ordinary shares in the foreseeable future\footnote{JD.com, Inc. annual report 2016, Page 131}.

\chapter{Share Capital and Reserves}

JD.com, Inc. holds outstanding shares consisting of ordinary shares, series A and A-1 convertible preferred shares and series B convertible preferred shares\footnote{JD.com, Inc. annual report 2016, Page F-10}.

\chapter{Current Assets and Current Liabilities}
\section{Current Assets}
A current asset is any asset which can reasonably be expected to be sold, consumed, or exhausted through the normal operations of a business within the current fiscal year. JD.com records 11 current assets accounts in its consolidated balance Sheet\footnote{JD.com, Inc. annual report 2016, Page F-3}.

We extract the following breakdown from JD.com, Inc. consolidated balance Sheet as of December 31, 2015 and as of December 31, 2016.\\

\begin{table}[H]	
\begin{center}
	\begin{tabular}{lrr}
		\toprule
		\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
		\midrule
		Cash and cash equivalents&17,863,868&19,771,695\\
		Restricted cash&2,114,913&4,391,955\\
		Short-term investments&2,780,482&4,391,955\\
		Investment securities&-&723,449\\
		Accounts receivable, net&8,193,665&17,464,408\\
		Advance to suppliers&927,177&1,423,736\\
		Inventories, net&20,539,543&28,909,438\\
		Loan receivables, net&3,698,488&12,697,915\\
		Other investments&-&10,766,920\\
		Prepayments and other current assets&1,486,441&2,198,906\\
		Amount due from related parties&863,516&1,410,050\\
		\qquad\emph{Total current assets}&58,468,093&106,932,098\\
		\bottomrule
	\end{tabular}
\end{center}
	\caption{Current assets (in thousands of RMB \textyen)}\label{table:1}
\end{table}
As we can see, the current assets jumped from \textyen58,468,093,000 to \textyen106,932,098,000.

\section{Current Liabilities}

We extract the following breakdown from JD.com, Inc. consolidated balance Sheet.\\

\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Short-term borrowings&17,863,868&19,771,695\\
			Nonrecourse securitization debt&2,114,913&4,391,955\\
			Accounts payable&2,780,482&4,391,955\\
			Advance from customers&-&723,449\\
			Deferred revenues&8,193,665&17,464,408\\
			Taxes payable&927,177&1,423,736\\
			Amount due to related parties&20,539,543&28,909,438\\
			Accrued expenses and other current liabilities&3,698,488&12,697,915\\
			Total current liabilities&-&10,766,920\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current liabilities (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\chapter{Inventories}
